### 2014-07-27 tex/GAME_HARD_01_CONTRIBUTION.tex
Cleaned up GNUplot script.

\begin{table*}
\parbox{.5\linewidth}{
\centering % Consider removing?
\caption{Average execution time in milliseconds\\of a $200\times 200$ integer matrix multiplication and\\corresponding percentage decrease- and increases.}
\label{tab:contribution:results:summaryint}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& \ah{hh1}{$1.16$}	& \ah{hf1}{\phantom{000}$0.24$}\ah{spc}{} 	& \ah{spc}{$-79.3\%$} \\ \hline \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& \ah{vh2}{}\ah{hh2}{$11610.02$}	& \ah{hf2}{$9866.40$}\ah{vh1}{}	& \ah{spc}{$-15.0\%$} \\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf2}{}\phantom{000}\ah{hh3}{$15.31$}	& \ah{hf3}{\phantom{00}$18.97$}\ah{vf1}{}	& \ah{spc}{$+23.9\%$} \\ \hline
        & \multicolumn{1}{|c|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|c|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
\end{tabular}
\arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
\arrow{hh2}{hf2}
\arrow{hh3}{hf3}
\arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
\arrow{vh2}{vf2}
}
\hfill
\parbox{.5\linewidth}{
\centering
\caption{Average execution time in milliseconds of\\a $200\times 200$ floating point matrix multiplication and\\ corresponding percentage decrease- and increases.}
\label{tab:contribution:results:summaryfloat}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& \ah{hh1}{$0.77$}	& \ah{hf1}{\phantom{0000}$0.22$}\ah{spc}{}	& \ah{spc}{$-71.4\%$} \\ \hline \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& \ah{vh1}{}\ah{hh2}{$10247.03$}	& \ah{hf2}{$10909.88$}\ah{vh2}{}	& \ah{spc}{$+6.5\%$} \\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf1}{}\phantom{000}\ah{hh3}{$14.08$}	& \ah{hf3}{\phantom{000}$17.44$}\ah{vf2}{}	& \ah{spc}{$+23.9\%$} \\ \hline
& \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
\end{tabular}
\arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
\arrow{hh2}{hf2}
\arrow{hh3}{hf3}
\arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
\arrow{vh2}{vf2}
}
\end{table*}

>>>>

\begin{table*}
\parbox{.5\linewidth}{
\centering % Consider removing?
\caption{Average execution time in milliseconds\\of a $200\times 200$ integer matrix multiplication and\\corresponding percentage decrease- and increases.}
\label{tab:contribution:results:summaryint}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& \ah{hh1}{$1.16$}	& \ah{hf1}{\phantom{000}$0.24$}\ah{spc}{} 	& \ah{spc}{$-79.3\%$} \\ \hline \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& \ah{vh2}{}\ah{hh2}{$11610.02$}	& \ah{hf2}{$9866.40$}\ah{vh1}{}	& \ah{spc}{$-15.0\%$} \\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf2}{}\phantom{000}\ah{hh3}{$15.31$}	& \ah{hf3}{\phantom{00}$18.97$}\ah{vf1}{}	& \ah{spc}{$+23.9\%$} \\ \hline
        & \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
\end{tabular}
\arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
\arrow{hh2}{hf2}
\arrow{hh3}{hf3}
\arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
\arrow{vh2}{vf2}
}
\hfill
\parbox{.5\linewidth}{
\centering
\caption{Average execution time in milliseconds of\\a $200\times 200$ floating point matrix multiplication and\\ corresponding percentage decrease- and increases.}
\label{tab:contribution:results:summaryfloat}
\begin{tabular}{r|r|r|r|}
	\cline{2-3}
	& \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
	\multicolumn{1}{|l|}{\textbf{HARD}}	& \ah{hh1}{$0.77$}	& \ah{hf1}{\phantom{0000}$0.22$}\ah{spc}{}	& \ah{spc}{$-71.4\%$} \\ \hline \hline
	\multicolumn{1}{|l|}{\textbf{SOFT}}	& \ah{vh1}{}\ah{hh2}{$10247.03$}	& \ah{hf2}{$10909.88$}\ah{vh2}{}	& \ah{spc}{$+6.5\%$} \\ \hline
	\multicolumn{1}{|l|}{\textbf{WARP}}	& \ah{vf1}{}\phantom{000}\ah{hh3}{$14.08$}	& \ah{hf3}{\phantom{000}$17.44$}\ah{vf2}{}	& \ah{spc}{$+23.9\%$} \\ \hline
& \multicolumn{1}{|r|}{\ah{spc}{$-99.9\%$}} & \multicolumn{1}{|r|}{\ah{spc}{$-99.8\%$}} \\ \cline{2-3}
\end{tabular}
\arrow{hh1}{hf1} % Draw horizontal arrow heads to fletchlings.
\arrow{hh2}{hf2}
\arrow{hh3}{hf3}
\arrow{vh1}{vf1} % Draw vertical arrow heads to fletchlings.
\arrow{vh2}{vf2}
}
\end{table*}
